\qns{GAN and WGAN Compare and Contrast} \newline

In this question, you’ll implement the architecture for a Vanilla GAN and WGAN with gradient penalty. Please click the link to access the question: \href{https://drive.google.com/drive/folders/1N0JSBAgoGtbzgxn6p1Z1MlQuZb5Tph9U?usp=sharing}{Code For Question 4}. \textbf{We highly encourage students to use Google Colab for this project as we have built in all the functionality to work smoothly on Google Colab. We also encourage students to start this question early since running implementations for GAN and WGAN can take a long time!} For this question, please submit a .zip file your completed work to the Gradescope assignment titled "WGAN HW (Code)". \\
\textit{Note: Due to the convergence issues we discussed in Question 1, you may run into problems when training your GAN. Around Epoch 30 to 40, if you start noticing your synthetic faces start looking worse / less human-like, you may have run into a convergence issue so please rerun.}

\begin{enumerate}
    \qitem {Implement the architecture for Vanilla GAN}
    
    \sol{Look at 1\textunderscore GAN\textunderscore ANSWERS.ipynb for solutions}
    
    \qitem {Implement the architecture for WGAN with Gradient Penalty}
    
    \sol{Look at 2\textunderscore WGAN\textunderscore ANSWERS.ipynb for solutions}

    \qitem {You may have had to rerun the GAN implementation a few times since there might be errors with convergence due to the issues we discussed in Question 1. Did you ever need to rerun the WGAN with Gradient Penalty? How does this reaffirm the benefits of WGAN over GAN? Which model generated the best synthetic images?}

    \sol{While there is a chance that students may have run into convergence issues with WGAN, this happens very rarely. A correct answer includes key ideas discussed in Question 1 and Question 2. Furthermore, most students should have WGAN performing better in generating synthetic images. }
    
\end{enumerate}
